ChIP-seq example

### 2019-12-18 analysis/chipseq.Rmd
Made a few small revisions to the text in the chipseq analysis.

```{r run-smash}
res <- smash.poiss(counts,post.var = TRUE)
```

@@

To provide a "baseline" to compare against the SMASH estimates, we
retrieve the peaks identified in the same ChIP-seq data using the MACS
software. Again, these data should have been included with the git
repository you downloaded.

@@

This next plot shows the intensity functions estimated by SMASH
(orange line) and the Haar-Fisz method (dark blue line). The read
count data are depicted as light blue circles, in which the area of
each circle is scaled by the number of data points that fall within
each 1.6-kb "bin". (We show counts summarized within bins because
there are too many data points to plot them individually.)

The peaks identified by the MACS software are shown as red
triangles. (Specifically, these are the *mean positions* of the
identified peak intervals; the peak intervals are short enough that it
is not useful to show both the start and end positions of these
intervals.)

@@

Based on this plot, it is clear that the strongest Haar-Fisz and SMASH
intensity estimates align very closely with the peaks found by
MACS. Intriguingly, the SMASH estimates also suggest the presence of
several additional weaker peaks that were not identified by MACS.

>>>>

```{r run-smash, warning=FALSE}
res <- smash.poiss(counts,post.var = TRUE)
```

@@

To provide a "baseline" to compare against the SMASH estimates, we
retrieve the peaks identified in the same ChIP-seq data using the MACS
software. Again, these data should have been included with the git
repository you downloaded by following the instructions above.

@@

This next plot shows the intensity functions estimated by SMASH
(orange line) and the Haar-Fisz method (dark blue line). The read
count data are depicted as light blue circles, in which the area of
each circle is scaled by the number of data points that fall within
each 1.6-kb "bin". (We show counts summarized within bins because
there are too many data points to plot them individually.) The peaks
identified by the MACS software are shown as red triangles.
(Specifically, these are the *mean positions* of the identified peak
intervals; the peak intervals are short enough that it is not useful
to show both the start and end positions of these intervals.)

@@

Based on this plot, it is clear that the strongest Haar-Fisz and SMASH
intensity estimates align very closely with the peaks found by MACS,
although the Haar-Fisz method failed to replicate at least two of
the MACS peaks. Intriguingly, the SMASH estimates also suggest the
presence of several additional weaker peaks that were not identified
by MACS.
